Covid-19 Fields Survey Data Protocol

### 2023-01-13 protocol/Background_and_methods_Jan_12.tex
updatd models

\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Covid-19 Fields Survey Data Protocol},
  pdfauthor={Ariel Mundo Ortiz},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Covid-19 Fields Survey Data Protocol}
\author{Ariel Mundo Ortiz}
\date{1/12/23}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, borderline west={3pt}{0pt}{shadecolor}, interior hidden, frame hidden, enhanced, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

The original dataset contained 39,029 entries (where each entry
corresponded to a set of answers provided by a unique respondent).
Following a preliminary analysis to identify the missing rates across
the different answers within each entry, it was identified that many of
the answers had high missing rates (\textgreater80\%) (note that the
graph will be in the Appendix). Therefore, the dataset was cleaned in
order to contain only the independent variables of interest with the
lowest missing rates (Table~\ref{tbl-covariates}) and the dependent
variable.

@@

\hypertarget{statistical-model}{%
\subsection{Statistical model}\label{statistical-model}}

We used a fixed-effects logistic regression to estimate the probability
of vaccination depending on the socio-economic factors described in
Section~\ref{sec-socio-demographic-factors} and the Health Regions from
Section~\ref{sec-geographical-location}. We examined the interaction of
income and Health Region as it has been shown that there has been an
increase in income inequality within the provinces of Canada over
time\textsuperscript{\protect\hyperlink{ref-marchand2020}{22}}, and the
relatively recent implementation of the Health Regions motivated us to
explore if income disparity may be an important factor to consider
within each of the Health Regions. Our model appears in
Equation~\ref{eq-model}.

\begin{equation}\protect\hypertarget{eq-model}{}{
\log \frac{p\textrm{(vac)}}{1-p\textrm{(vac)}}= \beta_0+ \beta_{1}\textrm{(age group)} +\beta_{2} \textrm{ race} + \beta_3 \textrm{(Health Region} \times \textrm{income)} 
}\label{eq-model}\end{equation}

@@

@@

\hypertarget{tbl-descriptive-stats}{}
\begin{longtable}[]{@{}lcc@{}}
\caption{\label{tbl-descriptive-stats}Descriptive Statistics of the
Fields Covid-19 Survey}\tabularnewline
\toprule()
\textbf{Characteristic} & \textbf{no}, N = 1,000 & \textbf{yes}, N =
2,709 \\
\midrule()
\endfirsthead
\toprule()
\textbf{Characteristic} & \textbf{no}, N = 1,000 & \textbf{yes}, N =
2,709 \\
\midrule()
\endhead
\textbf{income\_ord} & & \\
15000\_24999 & 167 (34\%) & 326 (66\%) \\
25000\_39999 & 144 (31\%) & 316 (69\%) \\
40000\_59999 & 116 (25\%) & 348 (75\%) \\
60000\_89999 & 71 (17\%) & 343 (83\%) \\
over\_90000 & 251 (25\%) & 752 (75\%) \\
under\_15000 & 251 (29\%) & 624 (71\%) \\
\textbf{age\_group} & & \\
16\_24 & 230 (27\%) & 634 (73\%) \\
25\_34 & 193 (27\%) & 518 (73\%) \\
35\_44 & 136 (25\%) & 400 (75\%) \\
45\_54 & 130 (28\%) & 335 (72\%) \\
55\_64 & 80 (20\%) & 317 (80\%) \\
65\_and\_over & 231 (31\%) & 505 (69\%) \\
\textbf{Health\_Region} & & \\
Central & 224 (28\%) & 581 (72\%) \\
East & 135 (23\%) & 448 (77\%) \\
North East & 36 (34\%) & 71 (66\%) \\
North West & 6 (12\%) & 45 (88\%) \\
Toronto & 371 (28\%) & 953 (72\%) \\
West & 228 (27\%) & 611 (73\%) \\
\textbf{race} & & \\
arab\_middle\_eastern & 77 (35\%) & 141 (65\%) \\
black & 120 (39\%) & 186 (61\%) \\
east\_asian\_pacific\_islander & 72 (23\%) & 236 (77\%) \\
indigenous & 82 (38\%) & 134 (62\%) \\
latin\_american & 70 (38\%) & 112 (62\%) \\
mixed & 111 (34\%) & 213 (66\%) \\
other & 134 (34\%) & 255 (66\%) \\
south\_asian & 89 (23\%) & 294 (77\%) \\
white\_caucasian & 245 (18\%) & 1,138 (82\%) \\
\bottomrule()
\end{longtable}

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{multicol}
\usepackage{hhline}
\usepackage{hyperref}
\usepackage{placeins}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Covid-19 Fields Survey Data Protocol},
  pdfauthor={Ariel Mundo Ortiz},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Covid-19 Fields Survey Data Protocol}
\author{Ariel Mundo Ortiz}
\date{1/13/23}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, boxrule=0pt, enhanced, breakable, interior hidden]}{\end{tcolorbox}}\fi

@@

The original dataset contained 39,029 entries (where each entry
corresponded to a set of answers provided by a unique respondent).
Following a preliminary analysis to identify the missing rates across
the different answers within each entry, it was identified that many of
the answers had high missing rates (\textgreater80\%) (note that the
graph will be in the Appendix). Therefore, the dataset was cleaned in
order to contain only the independent variables of interest with the
lowest missing rates (Table~\ref{tbl-covariates}) and the dependent
variable. The final clean dataset contained 3,709 unique entries.

@@

\hypertarget{statistical-models}{%
\subsection{Statistical models}\label{statistical-models}}

Because of the binary outcome of the survey answer of our interest
(vaccination status as ``yes'' or ``no'') we used a fixed-effects
logistic regression to estimate the probability of vaccination depending
on the socio-economic factors described in
Section~\ref{sec-socio-demographic-factors} and the Health Regions from
Section~\ref{sec-geographical-location}. Previous studies have shown
that socio-economic factors, and their interactions are significant
predictors of intent of vaccination and vaccination
status\textsuperscript{\protect\hyperlink{ref-nguyen2022}{22}--\protect\hyperlink{ref-cnat2022a}{24}}.
At the same time in the case of Canada, others have indicated an ongoing
need of socio-economic information that can provide a rationale for the
disparities in vaccination observed within some racial
groups\textsuperscript{\protect\hyperlink{ref-cnat2022b}{25}}.

Therefore, we built different logistic regression models that accounted
for different levels of interaction between the available socio-economic
factors obtained from the Fields Covid survey. The different models are
described below.

\hypertarget{model-building-and-selection}{%
\subsubsection{Model building and
selection}\label{model-building-and-selection}}

The first model (\texttt{model1}) examined the interaction of income and
Health Region as it has been shown that there has been an increase in
income inequality within the provinces of Canada over
time\textsuperscript{\protect\hyperlink{ref-marchand2020}{26}}, and the
relatively recent implementation of the Health Regions motivated us to
explore if income disparity may be an important factor to consider
within each of the Health Regions.

The the model was fitted using the function \texttt{svyglm} from the
\texttt{survey} R package in order to incorporate the correction in
sampling probability obtained from raking. The model appears in
Equation~\ref{eq-model1}.

\begin{equation}\protect\hypertarget{eq-model1}{}{
\begin{aligned}
\log \left( \frac{p\textrm{(vac)}}{1-p\textrm{(vac)}} \right) = \beta_0+ \beta_{1}\textrm{(Age group)} +\beta_{2} \textrm{ Race} +\\ \beta_3 \textrm{ Health Region} + \beta_4 \textrm{ Income} + \beta_5\textrm{(Health Region} \times \textrm{Income)}
\end{aligned}
}\label{eq-model1}\end{equation}

@@

The second model (\texttt{model2}) incorporated an interaction effect
between age group and income to examine if a significant interaction
occured between these factors as well. The model appears in
Equation~\ref{eq-model2}.

\begin{equation}\protect\hypertarget{eq-model2}{}{
\begin{aligned}
\log \left( \frac{p\textrm{(vac)}}{1-p\textrm{(vac)}} \right) = \beta_0+ \beta_{1}\textrm{(Age group)} +\beta_{2} \textrm{ Race} + \beta_3 \textrm{ Health Region} + \\\beta_4 \textrm{ Income}+ \beta_5\textrm{(Health Region} \times \textrm{Income)} + \beta_6 \textrm{ (Age group} \times \textrm{Income)}
\end{aligned}
}\label{eq-model2}\end{equation}

A third model (\texttt{model3}) incorporated an interaction effect
between race and income, and appears in Equation~\ref{eq-model3}.

\begin{equation}\protect\hypertarget{eq-model3}{}{
\begin{aligned}
\log \left( \frac{p\textrm{(vac)}}{1-p\textrm{(vac)}} \right) = \beta_0+ \beta_{1}\textrm{(Age group)} +\beta_{2} \textrm{ Race} + \beta_3 \textrm{ Health Region} + \beta_4 \textrm{ Income}+\\ \beta_5\textrm{(Health Region} \times \textrm{Income)} + \beta_6 \textrm{ (Age group} \times \textrm{Income)} + \beta_7 \textrm{ (Race} \times \textrm{Income)}
\end{aligned}
}\label{eq-model3}\end{equation}

Although it could have been interesting to examine the interaction of
Health Region and Race, or 3-way interactions between socio-economic
factors (e.g., age,income,race), these models had singularity issues.
Next, we compared the AIC of the three models indicated above. The AICs
are very similar and appear in Table~\ref{tbl-AIC}.

\hypertarget{tbl-AIC}{}
\begin{table}
\caption{\label{tbl-AIC}AIC for the three models }\tabularnewline

\centering
\begin{tabular}[t]{rl}
\toprule
AIC & model\\
\midrule
3580.878 & model1\\
3614.465 & model2\\
3633.575 & model3\\
\bottomrule
\end{tabular}
\end{table}

@@

\hypertarget{tbl-descriptive-stats}{}
\begin{table}[H]

\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\begin{longtable}[c]{|p{2.35in}|p{1.21in}|p{1.27in}}

\caption{\label{tbl-descriptive-stats}Descriptive Statistics of the Fields Covid-19 Survey } \\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Variable}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{no,\ N\ =\ 1,000}}\textcolor[HTML]{000000}{\textsuperscript{\fontsize{11}{11}\selectfont{1}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{yes,\ N\ =\ 2,709}}\textcolor[HTML]{000000}{\textsuperscript{\fontsize{11}{11}\selectfont{1}}}} \\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}-}\endhead

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Income}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{15000\_24999}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{167\ (34\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{326\ (66\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{25000\_39999}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{144\ (31\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{316\ (69\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{40000\_59999}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{116\ (25\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{348\ (75\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{60000\_89999}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{71\ (17\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{343\ (83\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{over\_90000}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{251\ (25\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{752\ (75\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{under\_15000}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{251\ (29\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{624\ (71\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Age\_group}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{16\_24}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{230\ (27\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{634\ (73\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{25\_34}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{193\ (27\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{518\ (73\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{35\_44}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{136\ (25\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{400\ (75\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{45\_54}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{130\ (28\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{335\ (72\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{55\_64}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{80\ (20\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{317\ (80\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{65\_and\_over}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{231\ (31\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{505\ (69\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Health\_Region}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Central}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{224\ (28\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{581\ (72\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{East}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{135\ (23\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{448\ (77\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{North\ East}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{36\ (34\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{71\ (66\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{North\ West}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{6\ (12\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{45\ (88\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Toronto}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{371\ (28\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{953\ (72\%)}}} \\
